Beyond Simple Features: A Large-Scale Feature Search Approach to Unconstrained Face Recognition

### 2011-06-30 discussion.tex
Fixed figure sizes and added a bit more verbiage to the discussion

>>>>

At the same time, experiments with synthetic faces suggest that the underlying 
representations (particularly of the best three layer model) can indeed tolerate
significant variation in face pose, provided that adequately diverse training data
is available.  More generally, the steady progression towards larger 
and larger tolerance to variation when more processing layers are added to the 
model provides encouragement that hierarchical models such as these provide 
a promising path forward in the construction of transformation-invariant 
representations.

### 2011-06-30 results.tex
Tidy up
Fixed figure sizes and added a bit more verbiage to the discussion

\begin{figure*}[ht]
\centering 
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.9]{figures/within_roc.pdf}
  \label{fig:within_rocs}
} 
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.9]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}
\subfigure[\small{comparison with literature}]{
    \begin{tabular}{|c||c|c|c|c|}
\hline
%Reference & Kumar et al. ICCV09 \cite{kumar:iccv09} & Wolf et al. ACCV09 \cite{wolf:accv09} & Cao et al. CVPR10 \cite{cao2010face} & This paper \\
 & Kumar et al. & Wolf et al. & Cao et al. & \\
Reference & ICCV09 \cite{kumar:iccv09} & ACCV09 \cite{wolf:accv09} & CVPR10 \cite{cao2010face} & This paper\\
\hline\hline
Mean classification error & 14.7\%$\pm$1.2 & 13.2\%$\pm$0.3 & 15.5\%$\pm$0.5 & \bf{11.9\%$\pm$0.6} \\
\hline
\end{tabular}
\label{fig:table_soa}
}

\caption[]{{\bf ROC curves for various model sub-families on \emph{LFW}
    Restricted View 2.} Curves for \cite{wolf:accv09}, \cite{kumar:iccv09} and \cite{cao2010face} 
  are plotted in \ref{fig:megablend_rocs} for reference.  Plots are zoomed-in to
  facilitate comparison.}
\label{fig:roc_curves}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering 
\subfigure[\small{V1-like}]{
  \includegraphics[scale=0.65]{figures/nfaces_variation_NaturalBg_v1like_a_plus.pdf}
  \label{fig:nfaces_v1like}
} 
\subfigure[\small{HT-L2-1st}]{
  \includegraphics[scale=0.65]{figures/nfaces_variation_NaturalBg_ht1_1_l2_1st.pdf}
  \label{fig:nfaces_l2}
} 
\subfigure[\small{HT-L3-1st}]{
  \includegraphics[scale=0.65]{figures/nfaces_variation_NaturalBg_ht1_1_l3_1st.pdf}
  \label{fig:nfaces_l3}
}
\caption[]{{\bf Effect of number of synthetic faces to be discriminated, sorted by model}}
\label{fig:nfaces_by_model}
\end{figure*}

@@

\begin{figure*}[ht]
\centering 
% \subfigure[\small{no variation}]{
%   \includegraphics[scale=0.6]{figures/nfaces_variation0_by_model.pdf}
%   \label{fig:nfaces_var0}
% } 
\subfigure[\small{variation level 2}]{
  \includegraphics[scale=0.7]{figures/nfaces_variation2_by_model.pdf}
  \label{fig:nfaces_var2}
} 
\subfigure[\small{variation level 4}]{
  \includegraphics[scale=0.7]{figures/nfaces_variation4_by_model.pdf}
  \label{fig:nfaces_var4}
}
\subfigure[\small{variation level 6}]{
  \includegraphics[scale=0.7]{figures/nfaces_variation6_by_model.pdf}
  \label{fig:nfaces_var6}
}

@@

\begin{figure*}[ht]
\centering 
% \subfigure[\small{no variation}]{
%   \includegraphics[scale=0.45]{figures/bg_variation0_by_model.pdf}
%   \label{fig:bg_var0}
% } 
\subfigure[\small{variation level 2}]{
  \includegraphics[scale=0.55]{figures/bg_variation2_by_model.pdf}
  \label{fig:bg_var2}
} 
\subfigure[\small{variation level 4}]{
  \includegraphics[scale=0.55]{figures/bg_variation4_by_model.pdf}
  \label{fig:bg_var4}
}
\subfigure[\small{variation level 6}]{
  \includegraphics[scale=0.55]{figures/bg_variation6_by_model.pdf}
  \label{fig:bg_var6}
}

>>>>

\begin{figure*}[ht]
\centering
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.6]{figures/within_roc.pdf}
  \label{fig:within_rocs}
}
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.6]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}
\subfigure[\small{comparison with literature}]{
    \small{
    \begin{tabular}{|c||c|c|c|c|}
\hline
%Reference & Kumar et al. ICCV09 \cite{kumar:iccv09} & Wolf et al. ACCV09 \cite{wolf:accv09} & Cao et al. CVPR10 \cite{cao2010face} & This paper \\
 & Kumar et al. & Wolf et al. & Cao et al. & \\
Reference & ICCV09 \cite{kumar:iccv09} & ACCV09 \cite{wolf:accv09} & CVPR10 \cite{cao2010face} & This paper\\
\hline\hline
Mean classification error & 14.7\%$\pm$1.2 & 13.2\%$\pm$0.3 & 15.5\%$\pm$0.5 & \bf{11.9\%$\pm$0.6} \\
\hline
\end{tabular}
    }
\label{fig:table_soa}
}
\caption[]{{\bf ROC curves for various model sub-families on \emph{LFW}
    Restricted View 2.} Curves for \cite{wolf:accv09}, \cite{kumar:iccv09} and \cite{cao2010face}
  are plotted in \ref{fig:megablend_rocs} for reference.  Plots are zoomed-in to
  facilitate comparison.}
\label{fig:roc_curves}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
\subfigure[\small{V1-like}]{
  \includegraphics[scale=0.5]{figures/nfaces_variation_NaturalBg_v1like_a_plus.pdf}
  \label{fig:nfaces_v1like}
}
\subfigure[\small{HT-L2-1st}]{
  \includegraphics[scale=0.5]{figures/nfaces_variation_NaturalBg_ht1_1_l2_1st.pdf}
  \label{fig:nfaces_l2}
}
\subfigure[\small{HT-L3-1st}]{
  \includegraphics[scale=0.5]{figures/nfaces_variation_NaturalBg_ht1_1_l3_1st.pdf}
  \label{fig:nfaces_l3}
}
\caption[]{{\bf Effect of number of synthetic faces to be discriminated, sorted by model}}
\label{fig:nfaces_by_model}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
% \subfigure[\small{no variation}]{
%   \includegraphics[scale=0.6]{figures/nfaces_variation0_by_model.pdf}
%   \label{fig:nfaces_var0}
% }
\subfigure[\small{variation level 2}]{
  \includegraphics[scale=0.55]{figures/nfaces_variation2_by_model.pdf}
  \label{fig:nfaces_var2}
}
\subfigure[\small{variation level 4}]{
  \includegraphics[scale=0.55]{figures/nfaces_variation4_by_model.pdf}
  \label{fig:nfaces_var4}
}
\subfigure[\small{variation level 6}]{
  \includegraphics[scale=0.55]{figures/nfaces_variation6_by_model.pdf}
  \label{fig:nfaces_var6}
}

@@

\begin{figure*}[ht]
\centering
% \subfigure[\small{no variation}]{
%   \includegraphics[scale=0.45]{figures/bg_variation0_by_model.pdf}
%   \label{fig:bg_var0}
% }
\subfigure[\small{variation level 2}]{
  \includegraphics[scale=0.45]{figures/bg_variation2_by_model.pdf}
  \label{fig:bg_var2}
}
\subfigure[\small{variation level 4}]{
  \includegraphics[scale=0.45]{figures/bg_variation4_by_model.pdf}
  \label{fig:bg_var4}
}
\subfigure[\small{variation level 6}]{
  \includegraphics[scale=0.45]{figures/bg_variation6_by_model.pdf}
  \label{fig:bg_var6}
}
